---
title: "Baleen Whale Acoustic Analysis Report"
date: "Date created: `r format(Sys.time(), '%Y-%m-%d')`"
output: 
  word_document:
    reference_docx: word_styles_reference_01.docx
    fig_caption: TRUE
format: "pipe"

params:
  deployment: ""
  metadata: ""
  missing_data: 
  missing_data_start: 
  missing_data_end: 
always_allow_html: TRUE

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE) # sets global defaults

# load packages

library(pacman)
pacman::p_load(here, tidyverse, lubridate, readxl, kableExtra, tinytex, flextable, RColorBrewer,xlsx,crul,stringr,readr,yardstick)

# set dplyr not to display 'summarise' messages

options(dplyr.summarise.inform = FALSE)

# deployment name in metadata uses "-" instead of "_" 

deploymentm<-str_replace_all(params$deployment, "_", "-")

# input metadata

metadata<-read_csv(here("R code", "RMarkdown Report", "metadata", paste(params$metadata)))

# input data: presence table
csv_data<-read_csv(here("Results", params$deployment, paste(params$deployment,"_DPA_MB_Annotations_FINAL.csv", sep="")))

# clean up and summarize csv data

annotation_data<-csv_data %>%
  
  # parse dates, rename columns of interest, drop unneeded columns
  transmute(filedate = as_date(as.character(`Start date and time (UTC)`)), 
            species = Species, callcat = V25, calltype = `Call type`) %>% 
  
  # filter rows where species is unknown/uncertain
  mutate(unknownSp = startsWith(as.character(species),"UN")) %>% 
  filter(unknownSp =="FALSE") %>%
  
  # replace NA with 'none' so that it is treated as a factor level
  mutate(calltype = fct_explicit_na(calltype, na_level = "none")) %>%
  
  # bin by day and species/callcat/calltype combination
  group_by(filedate, species, callcat, calltype) %>%
  summarise() %>% 
  ungroup() 

# create named list of possible baleen whale species/call groups that may occur in data
spcallgroup_list <- c("BW_IF_all","BW_A_all","FW_IS_D","SW_FF_all","HB_all")
spcallgroup_label <- c("Blue whale (A/B/AB calls)","Blue whale (arch/downsweep calls)","Fin whale (20Hz calls)",
                   "Sei whale (full frequency downsweep calls)", "Humpback whale (all calls)")
names(spcallgroup_list) <-spcallgroup_label

```


```{r daily presence}

# set up metadata

deployment_metadata <- metadata %>%
  
  # select relevant deployment
  filter(Deployment==deploymentm) %>% 
  
  # set up latitude and longitude for cleaner output, format as numeric
  mutate(Latitude = format(Latitude, digits=4), Longitude = format(Longitude, digits=4)) %>% 
  mutate(Latitude = as.numeric(Latitude), Longitude = as.numeric(Longitude)) %>% 
  
  # parse dates and drop unneeded columns: start is first full recording day, end is last full recording day
  transmute(Deployment, Latitude, Longitude, start = as_date(`In-water_start`)+1, 
         end = as_date(`In-water_end`)-1) %>% 
  
  # get day of year for start and end, calculate number of days with effort
  mutate(start_day = yday(start), start_year = year(start), 
         end_day = yday(end), end_year = year(end),
         ndays = as.numeric(end - start+1))

# account for missing data if needed

if (params$missing_data){
  
  subdays <- as.numeric((params$missing_data_end - params$missing_data_start)+1)
  deployment_metadata <- deployment_metadata %>% 
    mutate(ndays = ndays-subdays)
  
  }

# sort out species/call groups

presence_data<-annotation_data %>% 
  mutate(spcallgroup = case_when(species=='BW' & callcat=='IF' ~ 'BW_IF_all',
                                 species=='BW' & callcat=='A' ~ 'BW_A_all',
                                 species=='FW' & callcat=='IS' ~ 'FW_IS_D',
                                 species=='SW' & callcat=='FF' ~ 'SW_FF_all',
                                 species=='HB' ~ 'HB_all')) %>%
  
  # remove rows that were not assigned a spcallgroup above
  drop_na(spcallgroup) %>% 
  
  # bin presence of each spcallgroup by day
  group_by(filedate, species, spcallgroup) %>%
  summarise() %>%
  ungroup() %>% 
  
  # remove days not included in effort (based on full 24-hour recordings)
  filter(filedate>=deployment_metadata$start) %>% 
  filter(filedate<=deployment_metadata$end) %>% 

  # add columns for year, month, and day of year
  mutate(year = factor(year(filedate))) %>%
  mutate(month = month(filedate)) %>% 
  mutate(day_of_year = lubridate::yday(filedate)) %>%
  
  # filter for spcallgroups of interest
  filter(spcallgroup %in% spcallgroup_list) %>%
  
  # add all spcallgroups of interest as factor levels
  mutate(spcallgroup = fct_expand(factor(spcallgroup), spcallgroup_list)) %>%  
  
  # rename factor levels
  mutate(spcallgroup = fct_recode(spcallgroup, !!!spcallgroup_list))

```

This report summarizes daily presence of baleen whale calls in the **`r deployment_metadata$Deployment`** dataset, deployed at `r deployment_metadata$Latitude`°N `r abs(deployment_metadata$Longitude)`°W and analyzed from `r deployment_metadata$start` to `r deployment_metadata$end` (`r deployment_metadata$ndays` days`r if(params$missing_data){paste0(", not including ", subdays, " days of missing data")}`).  

## Daily Presence Summary 


```{r daily_summary_table}

# summarize results for table
daily_summary<-presence_data %>% 
  group_by(spcallgroup) %>% 
  summarize(days_present = n()) %>%  
  mutate(percent_days_present = days_present/deployment_metadata$ndays*100) %>% 
  ungroup()

# specify column names
daily_col_names<-c("Species (call type) ", "Days present (#)", "Days present (%)")

# create table
daily_summary %>% 
  mutate_if(is.numeric, format, digits=2) %>% 
  flextable() %>% 
  set_header_df(mapping = data.frame(keys = colnames(daily_summary), values = daily_col_names, 
                                     stringsAsFactors = FALSE), key = "keys" ) %>%
  set_table_properties(layout = "autofit", width = 1) %>%
  theme_booktabs() %>% 
  font(fontname = "Segoe UI")
  
```
\
```{r fig1, fig.width=6.5, fig.cap="Daily presence of baleen whale calls"}
#add noise
noise_data<-csv_data %>%
  
  # parse dates, rename columns of interest, drop unneeded columns
  transmute(filedate = as_date(as.character(`Start date and time (UTC)`)), 
            species = Species, callcat = V25, calltype = `Call type`) %>% 
  filter(species %in% c("NC")& calltype ="TN") %>%
  select(filedate,species) %>% 
  mutate(species = "NC") %>% 
  group_by(filedate,species) %>%
  summarise() %>%
  ungroup() %>% 
  mutate(spcallgroup = '') %>% 
  
  # remove days not included in effort (based on full 24-hour recordings)
  filter(filedate>=deployment_metadata$start) %>% 
  filter(filedate<=deployment_metadata$end) %>% 
  
  # add columns for year, month, and day of year
  mutate(year = factor(year(filedate))) %>%
  mutate(month = month(filedate)) %>% 
  mutate(day_of_year = lubridate::yday(filedate))


# assign colors to species for plotting
#cols=c("#F8766D","#00BA38","#E76BF3","#619CFF")
#cols2 = brewer.pal(n = 5, name = "Dark2")
cols2 = c("#A6CEE3", "#1F78B4","#7570B3", "#E7298A", "#66A61E")
names(cols2) <- levels(presence_data$spcallgroup)

# set up missing data per year based on deployment metadata (for day of year axis)
no_data_periods <- tibble(starts = c(1, deployment_metadata$end_day+1),
                          ends = c(deployment_metadata$start_day-1, 366),
                          year = as_factor(c(deployment_metadata$start_year,
                                             deployment_metadata$end_year))) 

# if missing_data = TRUE, add additional missing data period
if (params$missing_data) {
  no_data_periods<-no_data_periods %>% 
    add_row(starts = yday(params$missing_data_start),
            ends = yday(params$missing_data_end),
            year = as_factor(year(params$missing_data_start)),
            start_dates = params$missing_data_start,
            end_dates = params$missing_data_end)
}
            

# create daily presence figure  
ggplot() +
  
  facet_wrap(~year, ncol=1) +
  
  # plot missing data periods using single geom_rect call - do this first so that years are in correct order
  geom_rect(data=no_data_periods, aes(xmin=starts,xmax=ends,ymin=-Inf, ymax=Inf), 
            fill = "grey50", colour = NA, alpha = 0.2) +
   
   #plot noise
  geom_tile(data=noise_data, aes(x=day_of_year, y=spcallgroup), height=Inf,
            fill = "gold", colour = NA, alpha = 0.2)+
  
  # plot species daily presence
  geom_tile(data=presence_data,aes(x=day_of_year, y=spcallgroup, fill = spcallgroup), height=0.75) + 
  
  # format plot
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.title.y=element_blank(),
        panel.grid.minor = element_blank(), 
        panel.grid.major.y= element_blank(), 
        panel.grid.major.x = element_blank(),
        panel.background = element_rect(fill= "white", colour = "grey50"),
        axis.text = element_text(size = 12), 
        axis.text.x = element_text(angle = 0, vjust=0, hjust=-0.5),
        axis.title.x = element_blank(),
        strip.text.x = element_text(size = 12,face = "bold"), 
        strip.background =element_rect(fill="white", colour = "black"),
        panel.border = element_rect(fill = NA, colour = "black"),
        plot.margin = margin(0.1,0.1,0.1,0.1,"cm"),
        legend.position = "bottom",
        legend.justification = "left",
        legend.direction = "vertical",
        legend.margin=margin(t=-10)) +
  
  # format x axis breaks by month
  scale_x_continuous(expand=c(0,0), limits=c(0, 367),
                     breaks = c(1, 32, 60, 91, 121, 152, 182, 213, 244, 274, 305, 335),
                     labels = c('Jan','Feb','Mar','Apr','May','Jun','Jul','Aug','Sep','Oct','Nov','Dec')) +
  
  # set y axis direction to match legend
  scale_y_discrete(limits = rev) +
  
  # format fill colors and legend
   scale_fill_manual(values = cols2,
                       name="",
                       drop = T) +
  
  guides(fill=guide_legend(ncol=2)) +
  
  xlab("")

```
\
\
**Figure 1:** Daily presence of baleen whale calls in the `r deployment_metadata$Deployment` dataset. Yellow shading indicates the annotated presence of anthropogenic noise (i.e., seismic pulses, vessel noise, mooring noise, etc.).
\
\
```{r fig2, fig.width=5, fig.height=6, fig.cap="Weekly presence of baleen whale calls"}


# get number of effort days per week from deployment metadata
weekly_effort <- tibble(effort_date = seq.Date(deployment_metadata$start,
                           deployment_metadata$end,by=1)) %>% 
  mutate(year = factor(year(effort_date))) %>%
  mutate(weekstart = floor_date(effort_date, "weeks")) %>% 
  group_by(year, weekstart) %>% 
  summarise(days_effort = n()) %>% 
  ungroup()

# set up missing data per year based on deployment metadata (for date axis)
no_data_periods2 <- tibble(year = as_factor(c(deployment_metadata$start_year,
                                             deployment_metadata$end_year)),
                           startdates = c(as.Date(paste0(deployment_metadata$start_year, "-01-01")), deployment_metadata$end),
                           enddates = c(deployment_metadata$start-1, as.Date(paste0(deployment_metadata$end_year, "-12-31"))))

# get presence days per week and join with effort
days_per_week <- presence_data %>% 
  mutate(weekstart = floor_date(filedate, "weeks")) %>% 
  group_by(spcallgroup, year, weekstart) %>% 
  summarise(days_present = n()) %>% 
  left_join(weekly_effort,by=c("year","weekstart")) %>% 
  mutate(proportion_days_present = days_present/days_effort) %>% 
  ungroup()

#get weekly noise
noise_per_week <- noise_data %>% 
  mutate(weekstart = floor_date(filedate,"weeks")) %>% 
  group_by(spcallgroup, year, weekstart) %>% 
  mutate(days_present = 7) %>% 
  full_join(weekly_effort,by=c("year","weekstart")) %>% 
  mutate(proportion_days_present = days_present/days_effort) %>% 
  ungroup() %>% 
  select(year,weekstart,days_present,days_effort,proportion_days_present)

# create weekly presence figure
ggplot() +
  
  #plot noise
  geom_tile(data=noise_per_week, aes(x=weekstart, y=days_present), height=Inf,
            fill = "gold", colour = NA, alpha = 0.1, width=7)+
  
  # facet by species 
  facet_wrap(~spcallgroup, ncol = 1) + 
  
  # add no data periods 
  geom_rect(data = no_data_periods2, aes(xmin = startdates, xmax = enddates, ymin = -Inf, ymax = Inf),
            fill = "grey50", colour = NA, alpha = 0.2) +
  
  # add bar plot of number of days per week
  geom_col(data = days_per_week, aes(x = weekstart, y = days_present, fill = spcallgroup), 
           show.legend = F, width=4) + 
  
  # format fill colors and legend
   scale_fill_manual(values = cols2,
                       name="Species/call type",
                       drop = T) +
  
  scale_y_continuous(expand = c(0,0), limits = c(0,7)) +
  
  scale_x_date(date_label="%b %Y", expand = c(0,0)) +
  
  theme(panel.grid.minor = element_blank(),
        panel.grid.major =element_blank(),
        panel.background = element_rect(fill= "white", colour = "grey50"), 
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 11, face = "bold"),
        strip.text.x = element_text(size = 11, face = "bold"), 
        strip.background =element_rect(fill="white", colour = "grey50"), 
        panel.border = element_rect(fill = NA, colour = "grey60"),
        plot.margin = margin(0.5,0.5,0.5,0.5,"cm")) + 
  
  xlab("") + 
  
  ylab("Days per week")
  
```
\
**Figure 2:** Number of days per week with baleen whale call presence in the `r deployment_metadata$Deployment` dataset. Yellow shading indicates the annotated presence of anthropogenic noise (i.e., seismic pulses, vessel noise, mooring noise, etc.).
\

## Detector Performance
\
These are summary tables of the LFDCS detector performance for `r deployment_metadata$Deployment` at the file and daily level, for both detection tiers, for each species. **Note:** Recall values are calculated based on files and days opened as part of the presence analysis of the other species.
\
\
\
**Table 1:** LFDCS detector performance per file, per tier, for each species for the `r deployment_metadata$Deployment` dataset.
```{r detector_performance_table_file}
Detections <- read_csv(here('Validation',params$deployment,'ArkLite Inputs',paste0(params$deployment,'_MBDetections.csv')), show_col_types = FALSE)

detections_file <-Detections %>%
  mutate(filename=Filename) %>% 
  mutate(BW3 = case_when((Species=="Bm" & MD3 >0)~1,TRUE~0),
         BW4 = case_when((Species=="Bm" & MD4 >0)~1,TRUE~0),
         FW2 = case_when((Species=="Bp" & MD2 >0)~1,TRUE~0),
         FW3 = case_when((Species=="Bp" & MD3 >0)~1,TRUE~0),
         SW2 = case_when((Species=="Bb" & MD2 >0)~1,TRUE~0),
         SW4 = case_when((Species=="Bb" & MD4 >0)~1,TRUE~0),
         HB2 = case_when((Species=="Mn" & MD2 >0)~1,TRUE~0),
         HB3 = case_when((Species=="Mn" & MD3 >0)~1,TRUE~0)) %>%
  select(!c(Species,MD2, MD3, MD4)) %>%
  group_by(filename) %>%
  summarize(BW3 = sum(BW3), BW4 = sum(BW4),FW2 = sum(FW2), FW3=sum(FW3), 
            SW2= sum(SW2), SW4= sum(SW4), HB2=sum(HB2), HB3=sum(HB3)) %>%
  ungroup()

annotations_files <- csv_data %>%
  mutate(filename = str_extract(Soundfile, "[^\\\\]*$"), .after=Soundfile) %>% 
  mutate(BW = case_when(Species=='BW' & V25=='IF'~1,
                        is.na(Species)~ NA_real_,
                        TRUE~0),
         FW = case_when(Species=='FW' & V25=='IS'~1,
                        is.na(Species)~ NA_real_,
                        TRUE~0),
         SW = case_when(Species=='SW' & V25=='FF'~1,
                        is.na(Species)~ NA_real_,
                        TRUE~0),
         HB = case_when(Species=="HB"~1,
                        is.na(Species)~ NA_real_,
                        TRUE~0)) %>%
  select(!Species) %>%
  group_by(filename) %>%
  summarize(BW = sum(BW), FW = sum(FW), SW= sum(SW), HB=sum(HB)) %>%
  ungroup()

FileLFDCS <- left_join(detections_file, annotations_files, by ="filename") %>% 
  na.omit()

Filedata <- FileLFDCS %>% 
  filter(!if_any(BW:HB, ~.x %in% "?")) %>% 
  mutate_at(c('BW','FW','SW','HB'), as.numeric) %>% 
   mutate(BW = case_when(BW>0 ~ 1, TRUE~0),
         FW = case_when(FW>0 ~ 1, TRUE~0),
         SW = case_when(SW>0 ~ 1, TRUE~0),
         HB = case_when(HB>0 ~ 1, TRUE~0))

TableFileLFDCS<-data.frame(matrix(nrow=8, ncol=6, 0)) %>% 
  `colnames<-`(c("Precision","Recall","MCC","Nfiles","NfileswAnn","Nfileswdetec")) %>% 
  `rownames<-`(c("BW3","BW4","FW2","FW3","SW2","SW4","HB2","HB3"))

TableFileLFDCS<- TableFileLFDCS %>%
  mutate(Nfiles = nrow(Filedata),
         Nfileswdetec = case_when(rownames(TableFileLFDCS) == "BW3"~ sum(Filedata[, "BW3"]),
                                  rownames(TableFileLFDCS) == "BW4"~ sum(Filedata[, "BW4"]),
                                  rownames(TableFileLFDCS) == "FW2"~ sum(Filedata[, "FW2"]),
                                  rownames(TableFileLFDCS) == "FW3"~ sum(Filedata[, "FW3"]),
                                  rownames(TableFileLFDCS) == "SW2"~ sum(Filedata[, "SW2"]),
                                  rownames(TableFileLFDCS) == "SW4"~ sum(Filedata[, "SW4"]),
                                  rownames(TableFileLFDCS) == "HB2"~ sum(Filedata[, "HB2"]),
                                  rownames(TableFileLFDCS) == "HB3"~ sum(Filedata[, "HB3"])),
         NfileswAnn = case_when(rownames(TableFileLFDCS) == "BW3"~ sum(Filedata[, "BW"]),
                                rownames(TableFileLFDCS) == "BW4"~ sum(Filedata[, "BW"]),
                                rownames(TableFileLFDCS) == "FW2"~ sum(Filedata[, "FW"]),
                                rownames(TableFileLFDCS) == "FW3"~ sum(Filedata[, "FW"]),
                                rownames(TableFileLFDCS) == "SW2"~ sum(Filedata[, "SW"]),
                                rownames(TableFileLFDCS) == "SW4"~ sum(Filedata[, "SW"]),
                                rownames(TableFileLFDCS) == "HB2"~ sum(Filedata[, "HB"]),
                                rownames(TableFileLFDCS) == "HB3"~ sum(Filedata[, "HB"])))
Filedata2 <- Filedata %>% 
  mutate_if(sapply(Filedata, is.numeric),as.factor)
Filedata2<-Filedata2 %>% 
  mutate_if(sapply(Filedata2, is.factor), fct_rev)

TableFileLFDCS["BW3","Precision"] <- precision(Filedata2, "BW","BW3")[3]
TableFileLFDCS["BW4","Precision"] <- precision(Filedata2, "BW","BW4")[3]
TableFileLFDCS["FW2","Precision"] <- precision(Filedata2, "FW","FW2")[3]
TableFileLFDCS["FW3","Precision"] <- precision(Filedata2, "FW","FW3")[3]
TableFileLFDCS["SW2","Precision"] <- precision(Filedata2, "SW","SW2")[3]
TableFileLFDCS["SW4","Precision"] <- precision(Filedata2, "SW","SW4")[3]
TableFileLFDCS["HB2","Precision"] <- precision(Filedata2, "HB","HB2")[3]
TableFileLFDCS["HB3","Precision"] <- precision(Filedata2, "HB","HB3")[3]

TableFileLFDCS["BW3","Recall"] <- recall(Filedata2, "BW","BW3")[3]
TableFileLFDCS["BW4","Recall"] <- recall(Filedata2, "BW","BW4")[3]
TableFileLFDCS["FW2","Recall"] <- recall(Filedata2, "FW","FW2")[3]
TableFileLFDCS["FW3","Recall"] <- recall(Filedata2, "FW","FW3")[3]
TableFileLFDCS["SW2","Recall"] <- recall(Filedata2, "SW","SW2")[3]
TableFileLFDCS["SW4","Recall"] <- recall(Filedata2, "SW","SW4")[3]
TableFileLFDCS["HB2","Recall"] <- recall(Filedata2, "HB","HB2")[3]
TableFileLFDCS["HB3","Recall"] <- recall(Filedata2, "HB","HB3")[3]

TableFileLFDCS["BW3","MCC"] <- mcc(Filedata2, "BW","BW3")[3]
TableFileLFDCS["BW4","MCC"] <- mcc(Filedata2, "BW","BW4")[3]
TableFileLFDCS["FW2","MCC"] <- mcc(Filedata2, "FW","FW2")[3]
TableFileLFDCS["FW3","MCC"] <- mcc(Filedata2, "FW","FW3")[3]
TableFileLFDCS["SW2","MCC"] <- mcc(Filedata2, "SW","SW2")[3]
TableFileLFDCS["SW4","MCC"] <- mcc(Filedata2, "SW","SW4")[3]
TableFileLFDCS["HB2","MCC"] <- mcc(Filedata2, "HB","HB2")[3]
TableFileLFDCS["HB3","MCC"] <- mcc(Filedata2, "HB","HB3")[3]

## create table
# specify column names
file_names_old<- c("Species/Tier","Precision","Recall","MCC","Nfiles","NfileswAnn","Nfileswdetec") 
file_names_new <- c("Species/Tier","Precision","Recall","MCC Score","n Files","n Files w/Annotations", "n Files w/Detections")

TableFileLFDCS %>% 
  rownames_to_column(var="Species/Tier") %>% 
  as_tibble() %>% 
  mutate_if(is.numeric, format, digits=2) %>% 
  rename_at(vars(file_names_old),~file_names_new) %>% 
  flextable() %>% 
#  set_header_df(mapping = data.frame(keys = colnames(TableFileLFDCS), values = file_col_names, 
#                                    stringsAsFactors = FALSE), key = "keys" ) %>%
  set_table_properties(layout = "autofit", width = 1) %>%
  theme_booktabs() %>% 
  font(fontname = "Segoe UI")
```
\
**Table 2:** LFDCS detector performance per day, per tier, for each species for the `r deployment_metadata$Deployment` dataset.
```{r detector_performance_table_day}
detections_day <-Detections %>%
#  mutate(filename=Filename) %>% 
  mutate(BW3 = case_when((Species=="Bm" & MD3 >0)~TRUE, TRUE~0),
         BW4 = case_when((Species=="Bm" & MD4 >0)~TRUE, TRUE~0),
         FW2 = case_when((Species=="Bp" & MD2 >0)~TRUE, TRUE~0),
         FW3 = case_when((Species=="Bp" & MD3 >0)~TRUE, TRUE~0),
         SW2 = case_when((Species=="Bb" & MD2 >0)~TRUE, TRUE~0),
         SW4 = case_when((Species=="Bb" & MD4 >0)~TRUE, TRUE~0),
         HB2 = case_when((Species=="Mn" & MD2 >0)~TRUE, TRUE~0),
         HB3 = case_when((Species=="Mn" & MD3 >0)~TRUE, TRUE~0)) %>%
  select(!c(Species,MD2, MD3, MD4)) %>%
  group_by(Filename) %>%
  summarize(BW3 = sum(BW3), BW4 = sum(BW4),FW2 = sum(FW2), FW3=sum(FW3), 
            SW2= sum(SW2), SW4= sum(SW4), HB2=sum(HB2), HB3=sum(HB3)) %>%
  ungroup() %>%
 mutate(datestring = str_extract(Filename, "\\d{8}\\w\\d{6}\\w")) %>%
  mutate(Date = as_date(datestring, format="%Y%m%dT%H%M%SZ"))%>%
  drop_na() %>%
  group_by(Date)%>%
  summarize(BW3 = sum(BW3), BW4 = sum(BW4),FW2 = sum(FW2), FW3=sum(FW3), 
            SW2= sum(SW2), SW4= sum(SW4), HB2=sum(HB2), HB3=sum(HB3)) %>%
  ungroup()%>%
  complete(Date = seq.Date(deployment_metadata$start,deployment_metadata$end, by="day"),fill=list(BW3=0,BW4=0, FW2=0, FW3=0, SW2=0, SW4=0, HB2=0, HB3=0))

annotations_day <- csv_data %>%
  mutate(filename = str_extract(Soundfile, "[^\\\\]*$"), .after=Soundfile) %>% 
  mutate(BW = case_when(Species=='BW' & V25=='IF'~1,
                        is.na(Species)~ NA_real_,
                        TRUE~0),
         FW = case_when(Species=='FW' & V25=='IS'~1,
                        is.na(Species)~ NA_real_,
                        TRUE~0),
         SW = case_when(Species=='SW' & V25=='FF'~1,
                        is.na(Species)~ NA_real_,
                        TRUE~0),
         HB = case_when(Species=="HB"~1,
                        is.na(Species)~ NA_real_,
                        TRUE~0)) %>%
  select(!Species) %>%
  group_by(filename) %>%
  summarize(BW = sum(BW), FW = sum(FW), SW= sum(SW), HB=sum(HB)) %>%
  ungroup() %>% 
  mutate(datestring = str_extract(filename, "\\d{8}\\w\\d{6}\\w")) %>%
  mutate(Date = as_date(datestring, format="%Y%m%dT%H%M%SZ"))%>%
  drop_na() %>%
  group_by(Date)%>%
  summarize(BW = sum(BW), FW = sum(FW), SW= sum(SW), HB=sum(HB)) %>%
  ungroup()%>%
  complete(Date = seq.Date(deployment_metadata$start,deployment_metadata$end, by="day"),fill=list(BW=0, FW=0, SW=0, HB=0)) %>% 
  mutate(BW = case_when(BW >0 ~1,TRUE~0),
         FW = case_when(FW>0~1,TRUE~0),
         SW = case_when(SW>0~1,TRUE~0),
         HB = case_when(HB >0~1,TRUE~0))

DayLFDCS <-left_join(detections_day, annotations_day, by ="Date") %>% 
  na.omit()

Daydata <- DayLFDCS %>% 
  mutate(BW3 = case_when(BW3>0 ~ 1, TRUE~0),
         BW4 = case_when(BW4>0 ~ 1, TRUE~0),
         FW2 = case_when(FW2>0 ~ 1, TRUE~0),
         FW3 = case_when(FW3>0 ~ 1, TRUE~0),
         SW2 = case_when(SW2>0 ~ 1, TRUE~0),
         SW4 = case_when(SW4>0 ~ 1, TRUE~0),
         HB2 = case_when(HB2>0 ~ 1, TRUE~0),
         HB3 = case_when(HB3>0 ~ 1, TRUE~0))

TableDayLFDCS<-data.frame(matrix(nrow=8, ncol=6, 0)) %>% 
  `colnames<-`(c("Precision","Recall","MCC","Ndays","NdayswAnn","Ndayswdetec")) %>% 
  `rownames<-`(c("BW3","BW4","FW2","FW3","SW2","SW4","HB2","HB3"))

TableDayLFDCS<- TableDayLFDCS %>%
  mutate(Ndays = nrow(Daydata),
         Ndayswdetec = case_when(rownames(TableDayLFDCS) == "BW3"~ sum(Daydata[, "BW3"]),
                                  rownames(TableDayLFDCS) == "BW4"~ sum(Daydata[, "BW4"]),
                                  rownames(TableDayLFDCS) == "FW2"~ sum(Daydata[, "FW2"]),
                                  rownames(TableDayLFDCS) == "FW3"~ sum(Daydata[, "FW3"]),
                                  rownames(TableDayLFDCS) == "SW2"~ sum(Daydata[, "SW2"]),
                                  rownames(TableDayLFDCS) == "SW4"~ sum(Daydata[, "SW4"]),
                                  rownames(TableDayLFDCS) == "HB2"~ sum(Daydata[, "HB2"]),
                                  rownames(TableDayLFDCS) == "HB3"~ sum(Daydata[, "HB3"])),
         NdayswAnn = case_when(rownames(TableDayLFDCS) == "BW3"~ sum(Daydata[, "BW"]),
                                rownames(TableDayLFDCS) == "BW4"~ sum(Daydata[, "BW"]),
                                rownames(TableDayLFDCS) == "FW2"~ sum(Daydata[, "FW"]),
                                rownames(TableDayLFDCS) == "FW3"~ sum(Daydata[, "FW"]),
                                rownames(TableDayLFDCS) == "SW2"~ sum(Daydata[, "SW"]),
                                rownames(TableDayLFDCS) == "SW4"~ sum(Daydata[, "SW"]),
                                rownames(TableDayLFDCS) == "HB2"~ sum(Daydata[, "HB"]),
                                rownames(TableDayLFDCS) == "HB3"~ sum(Daydata[, "HB"])))
Daydata2 <- Daydata %>% 
  mutate_if(sapply(Daydata, is.numeric),as.factor)
Daydata2<-Daydata2 %>% 
  mutate(across(everything(), factor, levels = c("0","1"))) %>% 
  mutate_if(sapply(Daydata2, is.factor), fct_rev)

TableDayLFDCS["BW3","Precision"] <- precision(Daydata2, "BW","BW3")[3]
TableDayLFDCS["BW4","Precision"] <- precision(Daydata2, "BW","BW4")[3]
TableDayLFDCS["FW2","Precision"] <- precision(Daydata2, "FW","FW2")[3]
TableDayLFDCS["FW3","Precision"] <- precision(Daydata2, "FW","FW3")[3]
TableDayLFDCS["SW2","Precision"] <- precision(Daydata2, "SW","SW2")[3]
TableDayLFDCS["SW4","Precision"] <- precision(Daydata2, "SW","SW4")[3]
TableDayLFDCS["HB2","Precision"] <- precision(Daydata2, "HB","HB2")[3]
TableDayLFDCS["HB3","Precision"] <- precision(Daydata2, "HB","HB3")[3]

TableDayLFDCS["BW3","Recall"] <- recall(Daydata2, "BW","BW3")[3]
TableDayLFDCS["BW4","Recall"] <- recall(Daydata2, "BW","BW4")[3]
TableDayLFDCS["FW2","Recall"] <- recall(Daydata2, "FW","FW2")[3]
TableDayLFDCS["FW3","Recall"] <- recall(Daydata2, "FW","FW3")[3]
TableDayLFDCS["SW2","Recall"] <- recall(Daydata2, "SW","SW2")[3]
TableDayLFDCS["SW4","Recall"] <- recall(Daydata2, "SW","SW4")[3]
TableDayLFDCS["HB2","Recall"] <- recall(Daydata2, "HB","HB2")[3]
TableDayLFDCS["HB3","Recall"] <- recall(Daydata2, "HB","HB3")[3]

TableDayLFDCS["BW3","MCC"] <- mcc(Daydata2, "BW","BW3")[3]
TableDayLFDCS["BW4","MCC"] <- mcc(Daydata2, "BW","BW4")[3]
TableDayLFDCS["FW2","MCC"] <- mcc(Daydata2, "FW","FW2")[3]
TableDayLFDCS["FW3","MCC"] <- mcc(Daydata2, "FW","FW3")[3]
TableDayLFDCS["SW2","MCC"] <- mcc(Daydata2, "SW","SW2")[3]
TableDayLFDCS["SW4","MCC"] <- mcc(Daydata2, "SW","SW4")[3]
TableDayLFDCS["HB2","MCC"] <- mcc(Daydata2, "HB","HB2")[3]
TableDayLFDCS["HB3","MCC"] <- mcc(Daydata2, "HB","HB3")[3]


## Make a Table

day_names_old<- c("Species/Tier","Precision","Recall","MCC","Ndays","NdayswAnn","Ndayswdetec") 
day_names_new <- c("Species/Tier","Precision","Recall","MCC Score","n Days","n Days w/Annotations", "n Days w/Detections")

TableDayLFDCS %>% 
  rownames_to_column(var="Species/Tier") %>% 
  as_tibble() %>% 
  mutate_if(is.numeric, format, digits=2) %>% 
  rename_at(vars(day_names_old),~day_names_new) %>% 
  flextable() %>% 
#  set_header_df(mapping = data.frame(keys = colnames(TableFileLFDCS), values = file_col_names, 
#                                    stringsAsFactors = FALSE), key = "keys" ) %>%
  set_table_properties(layout = "autofit", width = 1) %>%
  theme_booktabs() %>% 
  font(fontname = "Segoe UI")
```