---
title: "Baleen Whale Acoustic Analysis Report"
date: "Date created: `r format(Sys.time(), '%Y-%m-%d')`"
output: 
  word_document:
    reference_docx: word_styles_reference_01.docx
    fig_caption: TRUE
format: "pipe"

params:
  deployment: ""
  metadata: ""
  Bm_audible: 
  missing_data: 
  missing_data_starts: 
  missing_data_ends: 
always_allow_html: TRUE

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE) # sets global defaults

# load packages
library(pacman)
pacman::p_load(here, tidyverse, lubridate, kableExtra, tinytex, flextable, RColorBrewer, crul, stringr, readr, yardstick)

# set dplyr not to display 'summarise' messages
options(dplyr.summarise.inform = FALSE)

# deployment name in metadata uses "-" instead of "_" 
deploymentm<-str_replace_all(params$deployment, "_", "-")

# input metadata
metadata<-read_csv(paste0(r"(R:\Science\CetaceanOPPNoise\CetaceanOPPNoise_2\PAM_metadata)","\\", params$metadata))

# input data: baleen whale daily presence csv
csv_data<-read_csv(paste0(r"(R:\Science\CetaceanOPPNoise\CetaceanOPPNoise_5\BaleenWhale_AcousticAnalysis\Deployments\)",deployment,
                            r"(\Results\)", paste(params$deployment,"_baleenwhale_dailypresence.csv", sep="")))

## create named list of possible baleen whale species/call groups that may occur in data
spcallgroup_vec <- c("Bm_A_all",
                     "Bm_IF_all",
                     "Bp_IS_D", 
                     "Mn_all",                     
                     "Bb_FF_all", 
                     "Ba_PT_all", 
                     "Eg_UP_U")

spcallgroup_label <- c("Blue whale (audible calls)",
                       "Blue whale (tonal calls)",
                       "Fin whale (20Hz calls)",
                       "Humpback whale (all calls)",                        
                       "Sei whale (full frequency downsweep calls)",
                       "Minke whale (pulse trains)",
                       "North Atlantic right whale (upcalls)")

names(spcallgroup_vec) <-spcallgroup_label

```


```{r daily presence}

## set up metadata

deployment_metadata <- metadata %>%
  
  # select relevant deployment
  filter(Deployment == deploymentm) %>% 
  
  # set up latitude and longitude for cleaner output, format as numeric
  mutate(latitude = as.numeric(format(Latitude, digits=4)),
         longitude = as.numeric(format(Longitude, digits=4))) %>% 
  
  # parse dates and drop unneeded columns: start is first full recording day, end is last full recording day
  transmute(deployment = Deployment,
            latitude,
            longitude,
            start = as_date(`In-water_start`)+1, 
            end = as_date(`In-water_end`)-1) %>%
  
  # get day of year for start and end, calculate number of days with effort
  mutate(start_day = yday(start), 
         start_year = year(start), 
         end_day = yday(end), 
         end_year = year(end),
         ndays = as.numeric(end - start+1))

## create data frame for no data periods to use later in plots; add missing data periods if needed

no_data_periods <- tibble(year = as_factor(c(deployment_metadata$start_year, deployment_metadata$end_year)),
                          start_dates = c(as.Date(paste0(deployment_metadata$start_year, "-01-01")), deployment_metadata$end),
                          end_dates = c(deployment_metadata$start-1, as.Date(paste0(deployment_metadata$end_year, "-12-31"))),
                          data_gap = 0) %>%
  # if missing_data = TRUE, add additional missing data period(s)
  {if (params$missing_data) rbind(., list(year = as_factor(year(missing_data_starts)),
                                          start_dates = as.Date(missing_data_starts),
                                          end_dates = as.Date(missing_data_ends),
                                          data_gap = rep_len(1,length.out = length(missing_data_starts)))) else .}
 
# if missing_data=TRUE, generate vector of missing dates, calculate number of missing days, and subtract from recording effort

if (params$missing_data){
  
  missing_dates_list <- mapply(seq.Date, as.Date(missing_data_starts), as.Date(missing_data_ends), by = 1)
  missing_dates <- tibble(effort_date = as.Date(unlist(missing_dates_list, use.names = FALSE)))
  
  # get total number of missing days
  subdays <- length(missing_dates$effort_date)
  
  # subtract missing days from total recording days
  deployment_metadata <- deployment_metadata %>%
    mutate(ndays = ndays-subdays)
}


## set up species presence data

presence_data<-csv_data %>%
  
  # include only definite presence
  filter(presence == "D") %>% 
  
  # sort out species/call groups
  mutate(spcallgroup = case_when(species == "Bm" & callcat == "A" ~ "Bm_A_all",
                                 species == "Bm" & callcat == "IF" ~ "Bm_IF_all",
                                 species == "Bp" & callcat == "IS" ~ "Bp_IS_D",
                                 species == "Mn" ~ "Mn_all",                                 
                                 species == "Bb" & callcat == "FF" ~ "Bb_FF_all",
                                 species == "Ba" ~ "Ba_PT_all",
                                 species == "Eg" ~ "Eg_UP_U")) %>%
  
  # remove rows that were not assigned a spcallgroup above
  drop_na(spcallgroup) %>% 
  
  # bin presence of each spcallgroup by day
  group_by(detecdate, species, spcallgroup) %>%
  summarise() %>%
  ungroup() %>% 
  
  # remove days not included in effort (based on full 24-hour recordings)
  filter(detecdate >= deployment_metadata$start) %>% 
  filter(detecdate <= deployment_metadata$end) %>% 
  
  # remove results from partial days included in missing data periods
  {if (params$missing_data) filter(., !(detecdate %in% missing_dates$effort_date)) else .} %>%
  
  # add columns for year, month, and day of year
  mutate(year = factor(year(detecdate))) %>%
  mutate(month = month(detecdate)) %>% 
  mutate(day_of_year = lubridate::yday(detecdate)) %>%
  
  # add all spcallgroups of interest as factor levels, using order specified in spcallgroup_vec
  mutate(spcallgroup = factor(spcallgroup, spcallgroup_vec)) %>% 
  
  # rename factor levels
  mutate(spcallgroup = fct_recode(spcallgroup, !!!spcallgroup_vec))


```

This report summarizes daily presence of baleen whale calls in the **`r deployment_metadata$deployment`** dataset, deployed at `r deployment_metadata$latitude`°N `r abs(deployment_metadata$longitude)`°W and analyzed from `r deployment_metadata$start` to `r deployment_metadata$end` (`r deployment_metadata$ndays` days`r if(params$missing_data){paste0(", not including ", subdays, " days of missing data")}`).  

## Daily Presence Summary 


```{r daily_summary_table}

# summarize results for table
daily_summary<-presence_data %>% 
  group_by(spcallgroup) %>% 
  summarize(days_present = n()) %>%  
  mutate(percent_days_present = days_present/deployment_metadata$ndays*100) %>% 
  ungroup()

# specify column names
daily_col_names<-c("Species (call type) ", "Days present (#)", "Days present (%)")

# set up table
daily_summary_table <- daily_summary %>% 
  mutate_if(is.numeric, format, digits=2) %>% 
  flextable() %>% 
  set_header_df(mapping = data.frame(keys = colnames(daily_summary), 
                                     values = daily_col_names, 
                                     stringsAsFactors = FALSE), 
                key = "keys" ) %>%
  set_table_properties(layout = "autofit", width = 1) %>%
  theme_booktabs() %>% 
  font(fontname = "Segoe UI")

# add footnote regarding blue whale audible calls if based on opportunistic annotations
if(params$Bm_audible==FALSE){
daily_summary_table <- footnote(daily_summary_table, 
                        i = 1, j = 1, ref_symbols = "1",
                        value = as_paragraph("Blue whale audible calls were annotated opportunistically during multispecies analysis"))
}

# produce table
daily_summary_table

  
```
\
```{r fig1, fig.width=6.5, fig.height=5, fig.cap="Daily presence of baleen whale calls"}

# assign colors to species for plotting
cols = c("#A6CEE3", "#1F78B4","#7570B3", "#E7298A", "#66A61E", "darkorange", "darkred")
names(cols) <- levels(presence_data$spcallgroup)

# create daily presence figure  
ggplot() +
  
  facet_wrap(~year, ncol = 1) +
  
  # plot missing data periods using single geom_rect call - do this first so that years are in correct order
  geom_rect(data = no_data_periods, 
            aes(xmin = yday(start_dates), xmax = yday(end_dates), ymin = -Inf, ymax = Inf), 
            fill = "grey45", 
            colour = NA, 
            alpha = 0.2) +
  
  # plot species daily presence
  geom_tile(data = presence_data, aes(x = day_of_year, y = spcallgroup, fill = spcallgroup), height = 0.75) + 
  
  # format plot
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.minor = element_blank(), 
        panel.grid.major.y = element_blank(), 
        panel.grid.major.x = element_blank(),
        panel.background = element_rect(fill = "white", colour = "grey50"),
        axis.text = element_text(size = 12), 
        axis.text.x = element_text(angle = 0, vjust=0, hjust = -0.5),
        axis.title.x = element_blank(),
        strip.text.x = element_text(size = 12,face = "bold"), 
        strip.background = element_rect(fill = "white", colour = "black"),
        panel.border = element_rect(fill = NA, colour = "black"),
        plot.margin = margin(0.1,0.1,0.1,0.1,"cm"),
        legend.position = "bottom",
        legend.justification = "left",
        legend.direction = "vertical",
        legend.margin = margin(t=-10)) +
  
  # format x axis breaks by month
  scale_x_continuous(expand = c(0, 0), 
                     limits = c(0, 367),
                     breaks = c(1, 32, 60, 91, 121, 152, 182, 213, 244, 274, 305, 335),
                     labels = c('Jan','Feb','Mar','Apr','May','Jun','Jul','Aug','Sep','Oct','Nov','Dec')) +
  
  # set y axis direction to match legend
  scale_y_discrete(limits = rev) +
  
  # format fill colors and legend
  scale_fill_manual(values = cols,
                    name = "",
                    drop = T) +
  
  guides(fill = guide_legend(ncol = 2)) +
  
  xlab("")


```
\
\
**Figure 1:** Daily presence of baleen whale calls in the `r deployment_metadata$deployment` dataset.`r if(params$Bm_audible == FALSE){paste0(" Note that blue whale audible call presence is based only on opportunistic annotations.")}`
\
\
```{r fig2, fig.width=6.5, fig.height=8, fig.cap="Weekly presence of baleen whale calls"}

# get effort days within deployment period
weekly_effort <- tibble(effort_date = seq.Date(deployment_metadata$start, deployment_metadata$end, by = 1)) %>%
  mutate(effort = 1)

# if missing_data=TRUE, remove missing dates
if (params$missing_data) {
  
  weekly_effort<-weekly_effort %>%
    mutate(effort = case_when(effort_date %in% missing_dates$effort_date ~ 0,
                              .default = 1))
}

# get number of days per week with effort
weekly_effort<-weekly_effort %>%
  mutate(weekstart = floor_date(effort_date, "weeks")) %>%
  group_by(weekstart) %>%
  summarise(days_effort = sum(effort)) %>%
  ungroup()

# get presence days per week and join with effort
days_per_week <- presence_data %>% 
  mutate(weekstart = floor_date(detecdate, "weeks")) %>% 
  group_by(spcallgroup, weekstart) %>% 
  summarise(days_present = n()) %>% 
  left_join(weekly_effort, by = "weekstart") %>% 
  mutate(proportion_days_present = days_present/days_effort) %>% 
  ungroup()


## create weekly presence figure
ggplot() +
  
  # facet by species 
  facet_wrap(~spcallgroup, ncol = 1) + 
  
  # add no data periods 
  geom_rect(data = no_data_periods, 
            aes(xmin = start_dates, xmax = end_dates, ymin = -Inf, ymax = Inf),
            fill = "grey50", 
            colour = NA, 
            alpha = 0.2) +
  
  # add bar plot of number of days per week with species presence
  geom_col(data = days_per_week, 
           aes(x = weekstart, y = days_present, fill = spcallgroup), 
           show.legend = F, 
           width = 4) + 
  
  # format fill colors and legend
  scale_fill_manual(values = cols,
                    name = "Species/call type",
                    drop = T) +
  
  scale_y_continuous(expand = c(0,0), limits = c(0,7)) +
  
  scale_x_date(date_label = "%b %Y", expand = c(0,0)) +
  
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.background = element_rect(fill = "white", colour = "grey50"), 
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 11, face = "bold"),
        strip.text.x = element_text(size = 11, face = "bold"), 
        strip.background = element_rect(fill = "white", colour = "grey50"), 
        panel.border = element_rect(fill = NA, colour = "grey60"),
        plot.margin = margin(0.5,0.5,0.5,0.5,"cm")) + 
  
  xlab("") + 
  
  ylab("Days per week")

```
\
**Figure 2:** Number of days per week with baleen whale call presence in the `r deployment_metadata$deployment` dataset.`r if(params$Bm_audible == FALSE){paste0(" Note that blue whale audible call presence is based only on opportunistic annotations.")}`
\

## Detector Performance

These are summary tables of the LFDCS detector performance for `r deployment_metadata$deployment` at the file and daily level, for both detection tiers, for each species. **Note:** Recall values are calculated based on files and days opened as part of the presence analysis of the other species.
\
\
**Table 1:** LFDCS detector performance per file, per tier, for each species for the `r deployment_metadata$deployment` dataset.
```{r detector_performance_table_file, message=FALSE}

Detections <- read_csv(paste0(r"(R:\Science\CetaceanOPPNoise\CetaceanOPPNoise_5\BaleenWhale_AcousticAnalysis\Deployments\)",params$deployment,r"(\Validation\Arklite_Inputs\)",paste0(params$deployment,'_MBDetections.csv')), show_col_types = FALSE)

detections_file <-Detections %>%
  mutate(filename=Filename) %>% 
  mutate(BW3 = case_when((Species=="Bm" & MD3 >0)~1,TRUE~0),
         BW4 = case_when((Species=="Bm" & MD4 >0)~1,TRUE~0),
         FW2 = case_when((Species=="Bp" & MD2 >0)~1,TRUE~0),
         FW3 = case_when((Species=="Bp" & MD3 >0)~1,TRUE~0),
         SW2 = case_when((Species=="Bb" & MD2 >0)~1,TRUE~0),
         SW4 = case_when((Species=="Bb" & MD4 >0)~1,TRUE~0),
         HB2 = case_when((Species=="Mn" & MD2 >0)~1,TRUE~0),
         HB3 = case_when((Species=="Mn" & MD3 >0)~1,TRUE~0)) %>%
  select(!c(Species,MD2, MD3, MD4)) %>%
  group_by(filename) %>%
  summarize(BW3 = sum(BW3), BW4 = sum(BW4),FW2 = sum(FW2), FW3=sum(FW3), 
            SW2= sum(SW2), SW4= sum(SW4), HB2=sum(HB2), HB3=sum(HB3)) %>%
  ungroup()

Annotations<-read_csv(paste0(r"(R:\Science\CetaceanOPPNoise\CetaceanOPPNoise_5\BaleenWhale_AcousticAnalysis\Deployments\)",deployment,
                            r"(\Results\)", paste(params$deployment,"_DPA_MB_Annotations_FINAL.csv", sep="")))

annotations_files <- Annotations %>%
  mutate(filename = str_extract(Soundfile, "[^\\\\]*$"), .after=Soundfile) %>% 
  mutate(BW = case_when(Species=='BW' & V25=='IF'~1,
                        is.na(Species)~ NA_real_,
                        TRUE~0),
         FW = case_when(Species=='FW' & V25=='IS'~1,
                        is.na(Species)~ NA_real_,
                        TRUE~0),
         SW = case_when(Species=='SW' & V25=='FF'~1,
                        is.na(Species)~ NA_real_,
                        TRUE~0),
         HB = case_when(Species=="HB"~1,
                        is.na(Species)~ NA_real_,
                        TRUE~0)) %>%
  select(!Species) %>%
  group_by(filename) %>%
  summarize(BW = sum(BW), FW = sum(FW), SW= sum(SW), HB=sum(HB)) %>%
  ungroup()

FileLFDCS <- left_join(detections_file, annotations_files, by ="filename") %>% 
  na.omit()

Filedata <- FileLFDCS %>% 
  filter(!if_any(BW:HB, ~.x %in% "?")) %>% 
  mutate_at(c('BW','FW','SW','HB'), as.numeric) %>% 
   mutate(BW = case_when(BW>0 ~ 1, TRUE~0),
         FW = case_when(FW>0 ~ 1, TRUE~0),
         SW = case_when(SW>0 ~ 1, TRUE~0),
         HB = case_when(HB>0 ~ 1, TRUE~0))

TableFileLFDCS<-data.frame(matrix(nrow=8, ncol=6, 0)) %>% 
  `colnames<-`(c("Precision","Recall","MCC","Nfiles","NfileswAnn","Nfileswdetec")) %>% 
  `rownames<-`(c("BW3","BW4","FW2","FW3","SW2","SW4","HB2","HB3"))

TableFileLFDCS<- TableFileLFDCS %>%
  mutate(Nfiles = nrow(Filedata),
         Nfileswdetec = case_when(rownames(TableFileLFDCS) == "BW3"~ sum(Filedata[, "BW3"]),
                                  rownames(TableFileLFDCS) == "BW4"~ sum(Filedata[, "BW4"]),
                                  rownames(TableFileLFDCS) == "FW2"~ sum(Filedata[, "FW2"]),
                                  rownames(TableFileLFDCS) == "FW3"~ sum(Filedata[, "FW3"]),
                                  rownames(TableFileLFDCS) == "SW2"~ sum(Filedata[, "SW2"]),
                                  rownames(TableFileLFDCS) == "SW4"~ sum(Filedata[, "SW4"]),
                                  rownames(TableFileLFDCS) == "HB2"~ sum(Filedata[, "HB2"]),
                                  rownames(TableFileLFDCS) == "HB3"~ sum(Filedata[, "HB3"])),
         NfileswAnn = case_when(rownames(TableFileLFDCS) == "BW3"~ sum(Filedata[, "BW"]),
                                rownames(TableFileLFDCS) == "BW4"~ sum(Filedata[, "BW"]),
                                rownames(TableFileLFDCS) == "FW2"~ sum(Filedata[, "FW"]),
                                rownames(TableFileLFDCS) == "FW3"~ sum(Filedata[, "FW"]),
                                rownames(TableFileLFDCS) == "SW2"~ sum(Filedata[, "SW"]),
                                rownames(TableFileLFDCS) == "SW4"~ sum(Filedata[, "SW"]),
                                rownames(TableFileLFDCS) == "HB2"~ sum(Filedata[, "HB"]),
                                rownames(TableFileLFDCS) == "HB3"~ sum(Filedata[, "HB"])))
Filedata2 <- Filedata %>% 
  mutate_if(sapply(Filedata, is.numeric),as.factor)
Filedata2<-Filedata2 %>% 
  mutate_if(sapply(Filedata2, is.factor), fct_rev)

TableFileLFDCS["BW3","Precision"] <- precision(Filedata2, "BW","BW3")[3]
TableFileLFDCS["BW4","Precision"] <- precision(Filedata2, "BW","BW4")[3]
TableFileLFDCS["FW2","Precision"] <- precision(Filedata2, "FW","FW2")[3]
TableFileLFDCS["FW3","Precision"] <- precision(Filedata2, "FW","FW3")[3]
TableFileLFDCS["SW2","Precision"] <- precision(Filedata2, "SW","SW2")[3]
TableFileLFDCS["SW4","Precision"] <- precision(Filedata2, "SW","SW4")[3]
TableFileLFDCS["HB2","Precision"] <- precision(Filedata2, "HB","HB2")[3]
TableFileLFDCS["HB3","Precision"] <- precision(Filedata2, "HB","HB3")[3]

TableFileLFDCS["BW3","Recall"] <- recall(Filedata2, "BW","BW3")[3]
TableFileLFDCS["BW4","Recall"] <- recall(Filedata2, "BW","BW4")[3]
TableFileLFDCS["FW2","Recall"] <- recall(Filedata2, "FW","FW2")[3]
TableFileLFDCS["FW3","Recall"] <- recall(Filedata2, "FW","FW3")[3]
TableFileLFDCS["SW2","Recall"] <- recall(Filedata2, "SW","SW2")[3]
TableFileLFDCS["SW4","Recall"] <- recall(Filedata2, "SW","SW4")[3]
TableFileLFDCS["HB2","Recall"] <- recall(Filedata2, "HB","HB2")[3]
TableFileLFDCS["HB3","Recall"] <- recall(Filedata2, "HB","HB3")[3]

TableFileLFDCS["BW3","MCC"] <- mcc(Filedata2, "BW","BW3")[3]
TableFileLFDCS["BW4","MCC"] <- mcc(Filedata2, "BW","BW4")[3]
TableFileLFDCS["FW2","MCC"] <- mcc(Filedata2, "FW","FW2")[3]
TableFileLFDCS["FW3","MCC"] <- mcc(Filedata2, "FW","FW3")[3]
TableFileLFDCS["SW2","MCC"] <- mcc(Filedata2, "SW","SW2")[3]
TableFileLFDCS["SW4","MCC"] <- mcc(Filedata2, "SW","SW4")[3]
TableFileLFDCS["HB2","MCC"] <- mcc(Filedata2, "HB","HB2")[3]
TableFileLFDCS["HB3","MCC"] <- mcc(Filedata2, "HB","HB3")[3]

## create table
# specify column names
file_names_old<- c("Species/Tier","Precision","Recall","MCC","Nfiles","NfileswAnn","Nfileswdetec") 
file_names_new <- c("Species/Tier","Precision","Recall","MCC Score","n Files","n Files w/Annotations", "n Files w/Detections")

TableFileLFDCS %>% 
  rownames_to_column(var="Species/Tier") %>% 
  as_tibble() %>% 
  mutate_if(is.numeric, format, digits=2) %>% 
  rename_at(vars(file_names_old),~file_names_new) %>% 
  flextable() %>% 
#  set_header_df(mapping = data.frame(keys = colnames(TableFileLFDCS), values = file_col_names, 
#                                    stringsAsFactors = FALSE), key = "keys" ) %>%
  set_table_properties(layout = "autofit", width = 1) %>%
  theme_booktabs() %>% 
  font(fontname = "Segoe UI")
```
\
**Table 2:** LFDCS detector performance per day, per tier, for each species for the `r deployment_metadata$deployment` dataset.
```{r detector_performance_table_day}
detections_day <-Detections %>%
#  mutate(filename=Filename) %>% 
  mutate(BW3 = case_when((Species=="Bm" & MD3 >0)~TRUE, TRUE~0),
         BW4 = case_when((Species=="Bm" & MD4 >0)~TRUE, TRUE~0),
         FW2 = case_when((Species=="Bp" & MD2 >0)~TRUE, TRUE~0),
         FW3 = case_when((Species=="Bp" & MD3 >0)~TRUE, TRUE~0),
         SW2 = case_when((Species=="Bb" & MD2 >0)~TRUE, TRUE~0),
         SW4 = case_when((Species=="Bb" & MD4 >0)~TRUE, TRUE~0),
         HB2 = case_when((Species=="Mn" & MD2 >0)~TRUE, TRUE~0),
         HB3 = case_when((Species=="Mn" & MD3 >0)~TRUE, TRUE~0)) %>%
  select(!c(Species,MD2, MD3, MD4)) %>%
  group_by(Filename) %>%
  summarize(BW3 = sum(BW3), BW4 = sum(BW4),FW2 = sum(FW2), FW3=sum(FW3), 
            SW2= sum(SW2), SW4= sum(SW4), HB2=sum(HB2), HB3=sum(HB3)) %>%
  ungroup() %>%
 mutate(datestring = str_extract(Filename, "\\d{8}\\w\\d{6}\\w")) %>%
  mutate(Date = as_date(datestring, format="%Y%m%dT%H%M%SZ"))%>%
  drop_na() %>%
  group_by(Date)%>%
  summarize(BW3 = sum(BW3), BW4 = sum(BW4),FW2 = sum(FW2), FW3=sum(FW3), 
            SW2= sum(SW2), SW4= sum(SW4), HB2=sum(HB2), HB3=sum(HB3)) %>%
  ungroup()%>%
  complete(Date = seq.Date(deployment_metadata$start,deployment_metadata$end, by="day"),fill=list(BW3=0,BW4=0, FW2=0, FW3=0, SW2=0, SW4=0, HB2=0, HB3=0))

annotations_day <- Annotations %>%
  mutate(filename = str_extract(Soundfile, "[^\\\\]*$"), .after=Soundfile) %>% 
  mutate(BW = case_when(Species=='BW' & V25=='IF'~1,
                        is.na(Species)~ NA_real_,
                        TRUE~0),
         FW = case_when(Species=='FW' & V25=='IS'~1,
                        is.na(Species)~ NA_real_,
                        TRUE~0),
         SW = case_when(Species=='SW' & V25=='FF'~1,
                        is.na(Species)~ NA_real_,
                        TRUE~0),
         HB = case_when(Species=="HB"~1,
                        is.na(Species)~ NA_real_,
                        TRUE~0)) %>%
  select(!Species) %>%
  group_by(filename) %>%
  summarize(BW = sum(BW), FW = sum(FW), SW= sum(SW), HB=sum(HB)) %>%
  ungroup() %>% 
  mutate(datestring = str_extract(filename, "\\d{8}\\w\\d{6}\\w")) %>%
  mutate(Date = as_date(datestring, format="%Y%m%dT%H%M%SZ"))%>%
  drop_na() %>%
  group_by(Date)%>%
  summarize(BW = sum(BW), FW = sum(FW), SW= sum(SW), HB=sum(HB)) %>%
  ungroup()%>%
  complete(Date = seq.Date(deployment_metadata$start,deployment_metadata$end, by="day"),fill=list(BW=0, FW=0, SW=0, HB=0)) %>% 
  mutate(BW = case_when(BW >0 ~1,TRUE~0),
         FW = case_when(FW>0~1,TRUE~0),
         SW = case_when(SW>0~1,TRUE~0),
         HB = case_when(HB >0~1,TRUE~0))

DayLFDCS <-left_join(detections_day, annotations_day, by ="Date") %>% 
  na.omit()

Daydata <- DayLFDCS %>% 
  mutate(BW3 = case_when(BW3>0 ~ 1, TRUE~0),
         BW4 = case_when(BW4>0 ~ 1, TRUE~0),
         FW2 = case_when(FW2>0 ~ 1, TRUE~0),
         FW3 = case_when(FW3>0 ~ 1, TRUE~0),
         SW2 = case_when(SW2>0 ~ 1, TRUE~0),
         SW4 = case_when(SW4>0 ~ 1, TRUE~0),
         HB2 = case_when(HB2>0 ~ 1, TRUE~0),
         HB3 = case_when(HB3>0 ~ 1, TRUE~0))

TableDayLFDCS<-data.frame(matrix(nrow=8, ncol=6, 0)) %>% 
  `colnames<-`(c("Precision","Recall","MCC","Ndays","NdayswAnn","Ndayswdetec")) %>% 
  `rownames<-`(c("BW3","BW4","FW2","FW3","SW2","SW4","HB2","HB3"))

TableDayLFDCS<- TableDayLFDCS %>%
  mutate(Ndays = nrow(Daydata),
         Ndayswdetec = case_when(rownames(TableDayLFDCS) == "BW3"~ sum(Daydata[, "BW3"]),
                                  rownames(TableDayLFDCS) == "BW4"~ sum(Daydata[, "BW4"]),
                                  rownames(TableDayLFDCS) == "FW2"~ sum(Daydata[, "FW2"]),
                                  rownames(TableDayLFDCS) == "FW3"~ sum(Daydata[, "FW3"]),
                                  rownames(TableDayLFDCS) == "SW2"~ sum(Daydata[, "SW2"]),
                                  rownames(TableDayLFDCS) == "SW4"~ sum(Daydata[, "SW4"]),
                                  rownames(TableDayLFDCS) == "HB2"~ sum(Daydata[, "HB2"]),
                                  rownames(TableDayLFDCS) == "HB3"~ sum(Daydata[, "HB3"])),
         NdayswAnn = case_when(rownames(TableDayLFDCS) == "BW3"~ sum(Daydata[, "BW"]),
                                rownames(TableDayLFDCS) == "BW4"~ sum(Daydata[, "BW"]),
                                rownames(TableDayLFDCS) == "FW2"~ sum(Daydata[, "FW"]),
                                rownames(TableDayLFDCS) == "FW3"~ sum(Daydata[, "FW"]),
                                rownames(TableDayLFDCS) == "SW2"~ sum(Daydata[, "SW"]),
                                rownames(TableDayLFDCS) == "SW4"~ sum(Daydata[, "SW"]),
                                rownames(TableDayLFDCS) == "HB2"~ sum(Daydata[, "HB"]),
                                rownames(TableDayLFDCS) == "HB3"~ sum(Daydata[, "HB"])))
Daydata2 <- Daydata %>% 
  mutate_if(sapply(Daydata, is.numeric),as.factor)
Daydata2<-Daydata2 %>% 
  mutate(across(everything(), factor, levels = c("0","1"))) %>% 
  mutate_if(sapply(Daydata2, is.factor), fct_rev)

TableDayLFDCS["BW3","Precision"] <- precision(Daydata2, "BW","BW3")[3]
TableDayLFDCS["BW4","Precision"] <- precision(Daydata2, "BW","BW4")[3]
TableDayLFDCS["FW2","Precision"] <- precision(Daydata2, "FW","FW2")[3]
TableDayLFDCS["FW3","Precision"] <- precision(Daydata2, "FW","FW3")[3]
TableDayLFDCS["SW2","Precision"] <- precision(Daydata2, "SW","SW2")[3]
TableDayLFDCS["SW4","Precision"] <- precision(Daydata2, "SW","SW4")[3]
TableDayLFDCS["HB2","Precision"] <- precision(Daydata2, "HB","HB2")[3]
TableDayLFDCS["HB3","Precision"] <- precision(Daydata2, "HB","HB3")[3]

TableDayLFDCS["BW3","Recall"] <- recall(Daydata2, "BW","BW3")[3]
TableDayLFDCS["BW4","Recall"] <- recall(Daydata2, "BW","BW4")[3]
TableDayLFDCS["FW2","Recall"] <- recall(Daydata2, "FW","FW2")[3]
TableDayLFDCS["FW3","Recall"] <- recall(Daydata2, "FW","FW3")[3]
TableDayLFDCS["SW2","Recall"] <- recall(Daydata2, "SW","SW2")[3]
TableDayLFDCS["SW4","Recall"] <- recall(Daydata2, "SW","SW4")[3]
TableDayLFDCS["HB2","Recall"] <- recall(Daydata2, "HB","HB2")[3]
TableDayLFDCS["HB3","Recall"] <- recall(Daydata2, "HB","HB3")[3]

TableDayLFDCS["BW3","MCC"] <- mcc(Daydata2, "BW","BW3")[3]
TableDayLFDCS["BW4","MCC"] <- mcc(Daydata2, "BW","BW4")[3]
TableDayLFDCS["FW2","MCC"] <- mcc(Daydata2, "FW","FW2")[3]
TableDayLFDCS["FW3","MCC"] <- mcc(Daydata2, "FW","FW3")[3]
TableDayLFDCS["SW2","MCC"] <- mcc(Daydata2, "SW","SW2")[3]
TableDayLFDCS["SW4","MCC"] <- mcc(Daydata2, "SW","SW4")[3]
TableDayLFDCS["HB2","MCC"] <- mcc(Daydata2, "HB","HB2")[3]
TableDayLFDCS["HB3","MCC"] <- mcc(Daydata2, "HB","HB3")[3]


## Make a Table

day_names_old<- c("Species/Tier","Precision","Recall","MCC","Ndays","NdayswAnn","Ndayswdetec") 
day_names_new <- c("Species/Tier","Precision","Recall","MCC Score","n Days","n Days w/Annotations", "n Days w/Detections")

TableDayLFDCS %>% 
  rownames_to_column(var="Species/Tier") %>% 
  as_tibble() %>% 
  mutate_if(is.numeric, format, digits=2) %>% 
  rename_at(vars(day_names_old),~day_names_new) %>% 
  flextable() %>% 
#  set_header_df(mapping = data.frame(keys = colnames(TableFileLFDCS), values = file_col_names, 
#                                    stringsAsFactors = FALSE), key = "keys" ) %>%
  set_table_properties(layout = "autofit", width = 1) %>%
  theme_booktabs() %>% 
  font(fontname = "Segoe UI")
```